---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sfaR

<!-- badges: start -->
<!-- badges: end -->

*sfaR* provides a set of tools (maximum likelihood and
maximum simulated likelihood) for various specifications of stochastic
frontier analysis.

Three categories of models are available in *sfaR*:

* **Classic Stochastic Frontier Model**: This model allows the estimation of 
the frontier for a cross-sectional or pooled data. 

* **Latent Class Stochastic Frontier Model** (LCM): This model accounts for 
technological heterogeneity by splitting the observations into a maximum number of five classes. The
classification operates based on a logit functional form that can be
specified using some covariates (namely, the separating variables allowing
the separation of observations in several classes). Only the half normal
distribution is available for the one-sided error term. Heteroscedasticity
in both error terms is possible. The choice of the number of classes can be
guided by several information criteria (i.e. AIC, BIC or HQIC).

* **Sample Selection Correction Stochastic Frontier Model**: This model solves the selection bias due to
the correlation between the two-sided errors terms in both the selection and the 
frontier equations, in the case of cross-sectional or pooled data.

## Installation

You can install the development version of sfaR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hdakpo/sfaR")
```

Install the current version on CRAN with

```{r}
install.packages("sfaR")
```


## Example

This subsection provides set of examples introducing some important features of *sfaR*.

```{r example}
library(sfaR)
## basic example code
```

